---
title: " Version control \n or \n \"paper_final_v2_oops_reallyfinal.docx\" no more"
author: "Tham, Wei Yang"
date: "1/27/2018"
output: revealjs::revealjs_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Current workflow

1. Someone inititates a project
1. After tasks are assigned - code + files are stored on your own computer
1. Sometimes data and files are stored on the lab Google Drive 
1. Code and data generally shared by email
1. Communication and keeping track of tasks - combination of email + team meetings

## Takeaway

- Code and data distributed over a bunch of personal computers that are connected by Gmail (and Google Drive when we feel like it) 
- Downsides
    + Idiosyncratic ways of coding and organizing code
    + Dependent on individuals to keep track of tasks
    + Hard to see what everyone else is doing
    + Digging up old discussions by email is hard (e.g. too many "Meeting" subject headings)
    
## What are the alternatives?

- "General" task management tools: [Trello](https://trello.com/), [Basecamp](https://basecamp.com/how-it-works)
    + I've don't know much about these
- Version control: **Git + Github**
    + Other options: Bitbucket
    
## Version control
- Saves versions of a project
- Like a computer game: save at different points along a quest, and load the game at any point in the past
- Git is a version control software, Github is an online version control repository

## Version control

```{r, eval = FALSE}
knitr::include_graphics("images/")
```

